---
title: "Untitled"
output: slidy_presentation
background-color: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#### Question 
Does environmental quality such as air pollution and tree cover have a relationship with education levels for US counties?

#### Data Sources  
- Education & Income: USDA Economic Research Services  
- Air quality: Centers for Diseas Control and Prevention
- Tree cover: USDA Forest Service

#### Key Variables  
- Education: Education attainment level in adults, ratio of % higher education to % high school completion or below (2015)
- Income: Median household income (2015)
- Air quality: Concentration of particulate matter 2.5 (2010)
- Tree cover: Percent area tree cover (2010)

#### Methods
From class: tidyr, dplyr, webscraping html, for loops for downloading and compiling data, linear regression, ggplot, functions, joins, regex data cleaning   
Outside class: reading excel files, spatial data, leaflet interactive maps, tigris package, spatial interpolation, choropleth maps
 

# Slide with R Output




## Slide with Plot

```{r pressure}
plot(pressure)
```

