---
title: "Untitled"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#### Question 
Does environmental quality such as air pollution, water pollution, and tree cover have a relationship with education levels for US counties?

##### Data Sources  
- Education & income: USDA Economic Research Services  
- Air quality: Centers for Diseas Control and Prevention
- Tree cover: USDA Forest Service

#### Key Variables  
- Education: Education attainment level in adults, ratio of above high school education and high school completion or below (2015)
- Income: Median houseshold income (2015)
- Air quality: Concentration of particulate matter 2.5
- Tree cover: Percent area tree cover

##### Methoods
From classs: tidyr, dplyr, reading html, for loops for downloading and compiling data, linear regression, ggplot   
Outside class: readxl, spatial data, leaflet interactive map


# Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

